---
title: "Alcohol vs Seat choice"
author: "veronica gonzalez"
date: "9/6/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Looking at the box plot, compared to the people that sit in the front consume less than the people who sit in the back who consume more alcohol. The median is at zero, and the median for those who sit in the middle is close to one or two. Looking at these calculations you can see that the people who sit in the back consume more. 

### get fancy  

```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Numerical Summarys 

In this data, the front mean is 1.8, for the middle it is 3.2. Lastly the back is 9.6. Stating that the back seats have a bigger mean than the others. That the back seats consume much more. 


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Looking at the anova test the pr results were 0.000116 stating that their all the same amount meaning that all the rows are the same. The back and the front row are different from each other. But the middle row has a larger consumption of alcohol. Compared to the back row, and the front row has a smaller consumption. Meaning, that all the rows are completely different from each other. 


```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

This shows us that the front and the back are different as well as the middle and the back. But the front and the middle are statistically not different 
## Conclusions



